HMM

### 2016-01-14 paper3.Rnw
missing parameter chart I think

Furthermore, the state occupancies based on the
Viterbi algorithm, which predicts the most likely sequence of movement
states based on observed movement results
\citep{zucchini_hidden_2009,langrock_flexible_2012} cannot predict
future movement patterns and cannot capture which latent states
panthers are likely to occupy depending on time of day from the time
homogeneous transitions (ie, the transition between all states are
constant through time).

@@

For some kinds of model predictions, the time homogeneous transition model can perform as good as the time inhomogeneous transition models in terms of estimating the states by the Viterbi algorithm (the tradition state prediction method) and can easily overlook more complicated models. The Viterbi algorithm predicts the most likely sequence of movement states based on the observations which allows the time homogenous transition model's prediction to capture the temporal heterogeneity from the observations. In general, the time homogeneous transition model gives the broader scope of movement pattern where as the time inhomogeneous transitions models gives a more realistic movement structure and future predictions. See Appendix.

>>>>

@@

For some kinds of model predictions, the time homogeneous transition model can perform as good as the time inhomogeneous transition models in terms of predicting the states by the Viterbi algorithm (the tradition state prediction method) and can easily overlook more complicated models. The Viterbi algorithm solves/predicts for the most likely/probable sequence of movement states based on the observations \citep{zucchini_hidden_2009,langrock_flexible_2012}. This approach allows the time homogenous transition model's prediction to capture the temporal heterogeneity from the observations. It is useful to predict missing data in the observation sequence but fail to future movements beyond the observations sequence. In general, the time homogeneous transition model gives the broader scope of movement pattern where as the time inhomogeneous transitions models gives a more realistic movement structure and future predictions.
